### 2021-04-04 Chapter-3/Chapter-3.tex
Updates from Overleaf

@@

\tool{} also finds that most side-channel
vulnerabilities leak very little information in practice, which confirms our
initial assumption.
However, \tool{} finds some vulnerabilities with severe
leakages. Prior research has confirmed that some of these
vulnerabilities can be exploited in real attacks.
With our tool, developers can
distinguish non-critical ``vulnerabilities'' from severe ones.

>>>>

During our evaluation process, we are interested in the following
aspects:
\begin{enumerate}
    \item Is \tool{} effective to detect side-channels in real-world crypto systems? (Effectiveness)
    \item How much performance overhead does the method introduce? (Performance)
    \item How effective are the design choices made by the tool method? (Design Choices)
\end{enumerate}

@@

The evaluated algorithms can be classified into two categories: symmetric
encryption and asymmetric encryption.
